Exploratory Analysis Reece C

### 2025-12-04 Exploratory Analysis Reece C.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

ggplot(long_df, aes(x = Date, y = value))

ggplot(full_merge, aes(x = Date, y = mean_pH)) +
  geom_smooth() + 
  labs(title = "title") +
  theme_bw()

>>>>

@@

ggplot(long_df, aes(x = Date, y = value)) +
  geom_point(size = 0.1) +
  facet_wrap(~ metric, scales = "free_y")

#ggplot(full_merge, aes(x = Date, y = mean_pH)) +
#  geom_smooth() + 
#  labs(title = "title") +
#  theme_bw()
